The analogy of the cohort-equations paradigm to the compartmental epidemic models

### 2021-05-18 cohort.tex
make rull for cohort work

The matrix form of the cohort framework consists of the following 3 steps.
\begin{enumerate}[step 1]
\item
write the cohort Eq. $I'=-V I$, with the initial condition $I(0)$, where the n-by-n matrix $V$ is the flow matrix of leaving infected compartments in \cite{van2002reproduction}.

\item 
finding the intrinsic infectiousness kernel by integrating the cohort Eq. and solving for its time evolution, thus
the solution would be $I(\tau) = \exp(-V\tau) I(0)$. The kernel will be 
$K(\tau) = F I(\tau)$, where $F$ is the matrix of new infections in the compartment framework.
Note that the n-by-n matrix $\exp(-V\tau)$ is the probability of being infected and stay infectious at time $\tau$, where
$\exp(-V\tau)=\sum_{n=0}^\infty \tau^n (-V)^n/n!$.

@@

\bibliography{../SIRlibrary}
\end{document}

>>>>

The matrix form of the cohort framework consists of the following 3 steps.
\begin{enumerate}[step 1]
\item
write the cohort Eq. 
\begin{equation}
\label{eq:cohort}
I'=-V I,
\end{equation}
 with the proper initial condition $I(0)$, where the n-by-n matrix $V$ is the flow matrix of leaving infected compartments in \cite{van2002reproduction}.

\item 
finding the intrinsic infectiousness kernel by integrating the cohort Eq. and solving for its time evolution, thus
the solution would be 
\begin{equation}
\label{eq:I}
I(\tau) = \exp(-V\tau) I(0).
\end{equation}
The kernel will be 
\begin{equation}
\label{eq:kernel}
K(\tau) = F I(\tau), 
\end{equation}
where $F$ is the matrix of new infections in the compartment framework.
Note that the n-by-n matrix $\exp(-V\tau)$ is the probability of being infected and stay infectious at time $\tau$, where
$\exp(-V\tau)=\sum_{n=0}^\infty \tau^n (-V)^n/n!$.

@@

\bibliography{SIRlibrary}
\end{document}
